Evaluating Sound Similarity Metrics for Differentiable, Iterative Sound-Matching

### 2025-08-21 main.tex
Updates from Overleaf

The heuristics in past works can be broadly split into two categories:
\begin{enumerate}
    \item Supervised (or inference) methods which use datasets of sound and parameter pairs to describe the generation objective. Often with a large number of input and output examples~\cite{engel2020ddsp,salimi2020make,yee2018automatic,esling2019flow}
    \item Unsupervised or \textit{direct sound optimization} methods~\cite{horner1993machine,mitchell2007evolutionary,yee2018automatic,vahidi2023mesostructures}. Usually require at most one target example, and a loss function that measures the difference between the target and synthesizer outputs. 
\end{enumerate}

>>>>

The heuristics in past works can be broadly split into two categories:
\begin{enumerate}
    \item Supervised (or inference) methods which use datasets of sound and parameter pairs to describe the generation objective, often with a large number of input and output examples~\cite{engel2020ddsp,salimi2020make,yee2018automatic,esling2019flow}
    \item Unsupervised or \textit{direct sound optimization} methods~\cite{horner1993machine,mitchell2007evolutionary,yee2018automatic,vahidi2023mesostructures}. Usually require at most one target example, and a loss function that measures the difference between the target and synthesizer outputs. 
\end{enumerate}

### 2025-08-21 revised_main.tex
Updates from Overleaf

\subsection{Supervised vs Iterative}
\label{sec:optimization}
% The goal of sound-matching is to find the optimal parameters $\theta^*$ that minimize the loss between the synthesizer output and the target sound. 
% \[
% \theta^* = \arg\min_{\theta} L(\theta,t)
% \]

% The \textit{heuristics} (i.e., how the parameters are approximated) used in past works can be broadly split into two categories:
% \begin{enumerate}
%     \item Direct optimization methods~\cite{horner1993machine,mitchell2007evolutionary,yee2018automatic,vahidi2023mesostructures}. This requires a target example, and a loss function that measures the difference between the target and synthesizer outputs. Given these two necessary pieces, direct optimization refers to the iterative generation of a sound output, measurement the distance between target and output, and applying updates to the parameters.

%     \item Supervised (or inference) methods which use datasets of sound corresponding parameters to learn the generation objective. Often with a large number of input and output examples and use of DNNs~\cite{engel2020ddsp,salimi2020make,yee2018automatic,esling2019flow}. Often, these models output their parameter predictions in a single step (or 1-shot).

% \end{enumerate}

>>>>

\subsection{Heuristics and Historical Framing}
\label{sec:optimization}

The choice of \textit{heuristics} is yet another important attribute sound-matching. The goal of sound-matching is to find the optimal parameters $\theta^*$ that minimize the loss between the synthesizer output and the target sound. 
\[
\theta^* = \arg\min_{\theta} L(\theta,t)
\]

The heuristics (i.e., how $\theta^*$ is approximated) used in past works can be broadly split into the two categories of \textit{direct optimization} and \textit{supervised}  (or inference) methods. Direct optimization refers to the iterative generation of a sound output, measurement of similarity between target and output, and application of updates to the parameters to maximize similarity (or minimize loss)~\cite{horner1993machine,mitchell2007evolutionary,yee2018automatic,vahidi2023mesostructures}; while supervised methods use large datasets of synthesizer sounds and corresponding parameters to learn the generation objective, commonly with the use of DNNs~\cite{engel2020ddsp,salimi2020make,yee2018automatic,esling2019flow}. These models often make their parameter predictions in a single step (or 1-shot).

Given the different attributes discussed thus far, Table~\ref{tab:summary} contains an overview of relevant literature, covering important works in sound-matching. A more detailed historical analysis of past and current trends in sound-matching can be discussed.
